Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?

### 2016-06-17 text/ms.tex
more text

\title{Can we detect galaxy assembly bias with group and clustering statistics of SDSS main sample of galaxies?}
\author{Mohammadjavad Vakili , others}

@@

\section{Method}
For our standard HOD modeling, HOD parameterization of cite[zheng07] is assumed. According to this parameterization, the occupation of the central galaxies follows a nearest-integer distribution, 
and the occupation of the satellite galaxies follows a Poisson distribution. The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the folllowing equations 
\begin{eqnarray}
\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
\end{eqnarray}

@@

Following CITE[HEARIN ETAL], the centrals

For sampling from the likelihood given, we use the affine-invariant MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).

>>>>

\title{Can we constrain galaxy assembly bias with group and clustering statistics of SDSS galaxies?}
\author{Mohammadjavad Vakili , others}

@@

\section{Method}
\subsection{Occupation modeling}
For our standard HOD modeling, HOD parameterization of cite[zheng07] is assumed. According to this parameterization, the occupation of the central galaxies follows a nearest-integer distribution, 
and the occupation of the satellite galaxies follows a Poisson distribution. The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the folllowing equations 
\begin{eqnarray}
\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
\end{eqnarray}

@@

In this decorated occupation model, the allowable range for the quantities $\delta N_{c,1}$ and $\delta N_{s,1}$ is given by 
\begin{eqnarray}
-\langle N_{c} | M_{h}\rangle \leq \delta N_{c} \leq \langle N_{c} | M_{h}\rangle
 , \label{eq:cen-bounds} \\
-\langle N_{s} | M_{h}\rangle \leq \delta N_{s} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
\end{eqnarray}
Afterwards, CITE[HEARIN2015] defines the assembly bias parameter $\mathcal{A}$ in the following way:
\begin{eqnarray}
\delta N_{\alpha , 1}(M_{h}) &=& \mathcal{A_\alpha} \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \\
\delta N_{\alpha , 1}(M_{h}) &=& \mathcal{A_\alpha} \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0,
\end{eqnarray}
where the subscript $\alpha = c , s$ for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs. \ref{eq:cen-bounds} and \ref{eq:sat-bounds}.  
\subsection{Observables}

\subsection{}
For sampling from the likelihood given, we use the affine-invariant MCMC sampler $\mathtt{emcee}$ (CITE[FORMAN-MACKEY]).
